\bf Manifold Clustering in the Generalized Random Dot Product Graph

### 2022-04-27 draft/draft.Rmd
still working ...

In this setting, although each manifold is in $d$-dimensional space, since the manifolds are one-dimensional, it is possible to consider an ordering of points sampled on the manifold. 
In the original latent space in which there is no noise, the condition for which community detection is possible via $\eta$-neighborhood graph clustering or single linkage clustering is each pair of adjacent order statistics on each manifold being less than $\delta$ apart.

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ one-dimensional manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min_{k \neq \ell} \min_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Let $A_n$ be the event such that $\max_k \max_i \|x_{(i+1)}^{(k)} - x_{(i)}^{(k)}\| < \delta$, where $x_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(A_n) > 1 - \epsilon$. 
\end{theorem}

@@

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| < \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for any $k \neq \ell$. 
Here, $y_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold plus its corresponding noise. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) > 1 - \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \GRDPG_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, single linkage clustering produces zero community detection error with high probability. 
\end{theorem}

>>>>

In this setting, although each manifold is in $d$-dimensional space, since the manifolds are one-dimensional, it is possible to consider an ordering of points sampled on the manifold. 
In the original latent space in which there is no noise, the condition for which community detection is possible via $\eta$-neighborhood graph clustering or single linkage clustering is satisfied if each pair of adjacent order statistics on each manifold is less than $\delta$ apart.

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ one-dimensional manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Let $A_n$ be the event such that $\max_k \max_i \|x_{(i+1)}^{(k)} - x_{(i)}^{(k)}\| < \delta$, where $x_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(A_n) > 1 - \epsilon$. 
\end{theorem}

@@

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| < \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for any $k \neq \ell$, where, $y_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold plus its corresponding noise. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) > 1 - \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \GRDPG_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then single linkage clustering produces zero community detection error with high probability as $n \to \infty$. 
\end{theorem}

### 2022-04-27 draft/draft.tex
still working ...

In this setting, although each manifold is in \(d\)-dimensional space,
since the manifolds are one-dimensional, it is possible to consider an
ordering of points sampled on the manifold. In the original latent space
in which there is no noise, the condition for which community detection
is possible via \(\eta\)-neighborhood graph clustering or single linkage
clustering is each pair of adjacent order statistics on each manifold
being less than \(\delta\) apart.

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ one-dimensional manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min_{k \neq \ell} \min_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Let $A_n$ be the event such that $\max_k \max_i \|x_{(i+1)}^{(k)} - x_{(i)}^{(k)}\| < \delta$, where $x_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(A_n) > 1 - \epsilon$. 
\end{theorem}

@@

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| < \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for any $k \neq \ell$. 
Here, $y_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold plus its corresponding noise. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) > 1 - \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \mathrm{GRDPG}_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, single linkage clustering produces zero community detection error with high probability. 
\end{theorem}

>>>>

In this setting, although each manifold is in \(d\)-dimensional space,
since the manifolds are one-dimensional, it is possible to consider an
ordering of points sampled on the manifold. In the original latent space
in which there is no noise, the condition for which community detection
is possible via \(\eta\)-neighborhood graph clustering or single linkage
clustering is satisfied if each pair of adjacent order statistics on
each manifold is less than \(\delta\) apart.

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ one-dimensional manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Let $A_n$ be the event such that $\max_k \max_i \|x_{(i+1)}^{(k)} - x_{(i)}^{(k)}\| < \delta$, where $x_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold. 
Then for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(A_n) > 1 - \epsilon$. 
\end{theorem}

@@

\begin{theorem}[Community detection for one-dimensional nonintersecting manifolds with noise]
\label{nonintersect-with-noise}
Suppose the same setup as in theorem \ref{nonintersect-no-noise}. 
Define $y_i = x_i + e_i$ and $B_n$ as the event such that $\|y_{(i+1)}^{(k)} - y_{(i)}^{(k)}\| < \|y_{(i)}^{(k)} - y_{(j)}^{(\ell)}\|$ for any $k \neq \ell$, where, $y_{(i)}^{(k)}$ is the $i^{th}$ order statistic on the $k^{th}$ manifold plus its corresponding noise. 
Then if $\max_i \|e_i\| < \delta / 3$, for any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that when $n > N$, $P(B_n) > 1 - \epsilon$. 
\end{theorem}

\begin{theorem}[Community detection for one-dimensional nonintersecting manifold block models]
\label{nonintersect-mbm}
Suppose we have the same setup as in theorem \ref{nonintersect-no-noise}. 
Let $p, q \geq 0$ such that $p + q = d$ where $d$ is the dimension of the range of each $g_k$. 
Suppose we draw $A \sim \mathrm{GRDPG}_{p,q}(X; \rho_n)$ for some sparsity parameter $\rho_n \in (0, 1]$, and let $\hat{X}$ be the ASE of $A$. 
Then single linkage clustering produces zero community detection error with high probability as $n \to \infty$. 
\end{theorem}
